---
title: "Programming"
author: "Your Name"
institute: "University of Kansas Medical Center"
date: 2026-07-23
format:
  html:
    toc: true
    toc-depth: 2
    code-block-bg: true
    theme: cosmo
execute:
  echo: true
  eval: false
---


```{r}
#| message: false
library(tibble)
library(dplyr)
library(purrr)

sleep_study <- tibble::tibble(
  steps = rnorm(10, 8000, 1500),
  sleep_hours = rnorm(10, 7, 1),
  mood_score = rnorm(10, 50, 10),
  memory_score = rnorm(10, 75, 8)
)
```

## Tier 1: `f_to_c()`

**Formula:** `C = (F - 32) * 5/9`

Write a function called `f_to_c()` that converts a temperature in Fahrenheit to
Celsius. Test it on `98.6` and `32`.

```{r}
f_to_c <- function(temp_f) {
  
}

```

---

## Tier 2: `steps_to_miles()`

**Formula:** `miles = steps * 2.5 / 5280` (average stride length of 2.5 ft,
5,280 ft per mile)

Write a function called `steps_to_miles()` that converts a step count to miles,
with a `digits` argument (defaulting to 1) that controls how many decimal places
the result is rounded to. Test it on `8000` steps with the default rounding, and
again with `digits = 3`.

```{r}
steps_to_miles <- function(steps, digits = ) {
  
}

```

---

## Tier 3: Apply `steps_to_miles()` with `purrr::map_dbl()`

Use `purrr::map_dbl()` to apply `steps_to_miles()` to the vector of daily steps
below, both on its own and as a new column in a data frame.

```{r}
daily_steps <- c(4200, 6100, 8000, 9800, 11500)

```

### Stretch goal: forwarding `digits` through `map_dbl()`

Any extra arguments added after the function name in `map_dbl()` get forwarded to
that function for **every** element -- the same forwarding idea as `...` from
Chapter 25.

Repeat the `map_dbl()` calls above, but this time pass `digits = 3` through to
`steps_to_miles()` for every element.

```{r}

```

---
